---
title: "office"
author: "Sherry Hu"
date: "5/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# libraries 
library(car)
library(olsrr)
library(schrute)
library(tibble)
library(forcats)
library(dplyr)
library(ggplot2)
library(tidytext)
library(stringr)
library(textdata)
library(tidyr)
```

```{r}
# load in data
transcripts <- schrute::theoffice
head(transcripts)

ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-17/office_ratings.csv')
head(ratings)
```

```{r}
nrow(transcripts)
```

* There are 55,130 lines said in all 9 seasons of The Office. 

```{r}
# make season and episode factors
# remove "" for parsing issues
transcripts %>% 
  mutate(season = as.integer(season),
         episode = as.integer(episode)) %>%
  mutate(character = str_remove_all(character, '"'))
```

# EDA 
```{r}
# average rating across 9 seasons 
ratings %>% 
  group_by(season) %>%
  summarise(avg_rating = mean(imdb_rating)) %>%
  ggplot(aes(season, avg_rating)) + 
  geom_line() + 
  scale_x_continuous(breaks =1:9) + 
  ggtitle("Average IMDB Rating for Seasons of The Office") + 
  xlab("Season") + ylab("Average IMDB Rating")
```

* We see a huge dip in average rating after season 7. An initial hunch is that this is due to Steve Carell (Michael Scott), the main character, leaving this season. 

```{r}
# ratings by episode 
ratings %>%
  mutate(title = fct_inorder(title),
         episode_number = row_number()) %>%
  ggplot(aes(episode_number, imdb_rating)) + 
  geom_line(group = 1) + 
  geom_point(aes(color = factor(season))) + 
  expand_limits(x = -8) + 
  geom_smooth(group = 1) +
  theme(axis.text.x = element_blank(), panel.grid.major.x = element_blank()) + 
  labs(x = "Episode number",
       y = "IMDB Rating",
       title = "Popularity of The Office episodes over time",
       subtitle = "Color represents season, size represents number of ratings")

# ratings by episode w/ labels 
ratings %>%
  mutate(title = fct_inorder(title)) %>%
  ggplot(aes(title, imdb_rating)) + 
  geom_line(group = 1) + 
  geom_point(aes(color = factor(season))) + 
  geom_text(aes(label = title), check_overlap = TRUE, hjust = 1) + 
  theme(axis.text.x = element_blank(), panel.grid.major.x = element_blank())
```

* This shows us ratings by episode. We note that the finale has the highest rating. The episode with the second highest rating is "Goodbye Michael", which was the last episode Carell was in. 

```{r}
# Looking at how many lines each character has
transcripts %>% count(character, sort = TRUE)
```

* Michael has the most lines across all seasons, followed by Dwight, Jim, and Pam. From this, we can get a slight sense of who the main characters are. 

* Note that Creed, who only says 396 lines across all seasons, is a character that is loved by a lot of people. Thus, when selecting characters, it may not be the best idea to just select the characters who say the most number of lines. 

```{r}
unique(sort(transcripts$character))
```

* Let's look at what characters are in the data. From the above list, we see that there are a lot of errors in spelling. For example, "Michael" and "Micahel" refer to the same character. We attempt to fix this to the best of our ability. 

```{r}
# fixing Michael errors 
transcripts$character[transcripts$character == "Micahel"] <- "Michael"
transcripts$character[transcripts$character == "Micael"] <- "Michael"
transcripts$character[transcripts$character == "Michae"] <- "Michael"
transcripts$character[transcripts$character == "Mihael"] <- "Michael"
transcripts$character[transcripts$character == "Miichael"] <- "Michael"
transcripts$character[transcripts$character == "Micheal"] <- "Michael"
transcripts$character[transcripts$character == "Michal"] <- "Michael"
transcripts$character[transcripts$character == "Michel"] <- "Michael"
transcripts$character[transcripts$character == "Michael "] <- "Michael"
transcripts$character[transcripts$character == "MIchael"] <- "Michael"
transcripts$character[transcripts$character == "M ichael"] <- "Michael"

# fixing Pam errors
transcripts$character[transcripts$character == "Pam "] <- "Pam"

# fixing Jim errors
transcripts$character[transcripts$character == "JIm"] <- "Jim"
transcripts$character[transcripts$character == "Jim "] <- "Jim"

# fixing Dwight errors
transcripts$character[transcripts$character == "Dwight "] <- "Dwight"
transcripts$character[transcripts$character == "Dwight."] <- "Dwight"
transcripts$character[transcripts$character == "DwightKSchrute"] <- "Dwight"

# fixing Angela errors
transcripts$character[transcripts$character == "\"Angela\""] <- "Angela"
transcripts$character[transcripts$character == "Anglea"] <- "Angela"
transcripts$character[transcripts$character == "Angel"] <- "Angela"
transcripts$character[transcripts$character == "Angels"] <- "Angela"

# fixing Ryan errors
transcripts$character[transcripts$character == "Ryan Howard"] <- "Ryan"

# fixing Andy errors
transcripts$character[transcripts$character == "sAndy"] <- "Andy"

# fixing Robert California errors
# transcripts$character[transcripts$character == "Robert"] <- "Robert California"

# fixing Stanley errors
transcripts$character[transcripts$character == "Stanely"] <- "Stanley"

# fixing Meredith errors
transcripts$character[transcripts$character == "Meridith"] <- "Meredith"

# fixing Darryl errors
transcripts$character[transcripts$character ==  "Darrly"] <- "Darryl"
transcripts$character[transcripts$character ==  "Darry"] <- "Darryl"
transcripts$character[transcripts$character ==  "Daryl"] <- "Darryl"
                          
# fixing Phyllis errors
transcripts$character[transcripts$character ==  "Phylis"] <- "Phyllis"
transcripts$character[transcripts$character ==  "Phyliss"] <- "Phyllis"

# fixing Holly errors
transcripts$character[transcripts$character ==  "Holy"] <- "Holly"

# fixing Todd Packer errors
transcripts$character[transcripts$character ==  "Sweeney Todd"] <- "Todd"

# fixing David Wallace errors
transcripts$character[transcripts$character ==  "David Wallcve"] <- "David Wallace"
transcripts$character[transcripts$character ==  "Dacvid Walalce"] <- "David Wallace"
transcripts$character[transcripts$character ==  "Dacvid Wallace"] <- "David Wallace"

# fixing Bob Vance errors
transcripts$character[transcripts$character ==  "Bob"] <- "Bob Vance"
transcripts$character[transcripts$character ==  "Bob Vance, Vance Refrigeration"] <- "Bob Vance"

# Character personalities stay consistent whether or not they're on the phone
transcripts$character[transcripts$character == "Michael [on phone]" ] <- "Michael"
transcripts$character[transcripts$character == "Pam [on phone]"] <- "Pam"
transcripts$character[transcripts$character ==  "Jan [on phone]"] <- "Jan"
transcripts$character[transcripts$character == "Dwight [on phone]"] <- "Dwight"

# D is mapped to Dwight because it's his nickname
transcripts$character[transcripts$character == "D"] <- "Dwight"

```

* Next, we would like to drop some characters. As shown above, filtering characters by the number of lines said may not be the best idea. Instead, we only keep characters who are listed as "Main Characters" or "Supporting Characters" on this official wiki page for The Office: https://theoffice.fandom.com/wiki/Main_Characters. 

```{r}
# list of characters we want
included_characters <- c("Michael", "Dwight", "Jim", "Pam", "Ryan", "Andy", "Robert", "Angela", "Stanley", "Kevin", "Creed", "Meredith", "Kelly", "Erin", "Toby", "Oscar", "Darryl", "Phyllis", "Gabe", "Holly", "Jan", "Roy", "Todd", "David Wallace", "Karen", "Bob Vance", "Nellie")

# only keep row if it is in the list
transcripts <- transcripts[ transcripts$character %in% included_characters, ]

# confirm that we know have only the characters we want
unique(transcripts$character)
```

```{r}
# new size of data
nrow(transcripts)
```

* The dataset decreases from 55,130 lines to 49,125. We see that the included characters say roughly 89.1% of the lines in the whole show. 

```{r}
# obtain number of lines said by each character 
# put into dataframe called line_counts

line_counts <- transcripts %>% 
  group_by(season, episode, character) %>%
  count(character)

# change data to format we want
line_counts <- pivot_wider(line_counts, names_from = character, values_from = n)
line_counts[is.na(line_counts)] <- 0

# change column names
colnames(line_counts) <- paste("lines", colnames(line_counts), sep="_")
colnames(line_counts)[1] <- "season"
colnames(line_counts)[2] <- "episode"

head(line_counts)
```

* We obtain number of lines said by the characters we care about in each episode. 

```{r}
# split sentences into words using unnest
transcript_words <- transcripts %>% 
  dplyr::select(-text_w_direction) %>%
  unnest_tokens(word, text)

head(transcript_words)
```

* Next, we want to look at average sentiment score of a character per episode. First, we tokenize the lines into words. 

```{r}
# function returns a column of sentiment scores given a column of words
sentiments_data <- transcript_words %>% 
  left_join(get_sentiments("afinn")) %>%                 # get sentiment scores from AFINN
  mutate(value = if_else(is.na(value), 0, value)) %>%    # make NA's -> 0 
  group_by(season, episode, character) %>% 
  summarize(avg_s = mean(value, na.rm = TRUE))           # gives us each character's avg sentiment per episode

sentiments_data <- pivot_wider(sentiments_data, names_from = character, values_from = avg_s )   # change data to format we want
sentiments_data[is.na(sentiments_data)] <- 0      # replace NA's w/ 0 (avg sentiment = 0 for absent characters)

# fix column names
colnames(sentiments_data) <- paste("s", colnames(sentiments_data), sep="_")
colnames(sentiments_data)[1] <- "season"
colnames(sentiments_data)[2] <- "episode"

head(sentiments_data)
```

* We get our desired dataset, with average sentiment score of each character per episode. 

```{r}
# first, reformat ratings from transcripts to merge properly
ratings <- transcripts %>%
  group_by(episode, season) %>%
  summarize(rating = median(imdb_rating),
  num_voters = median(total_votes))

# merge datasets
data <- merge(line_counts, sentiments_data, by=c("season","episode"))
data <- merge(data, ratings, by=c("season", "episode"))

# change season/episode to categorical variables
data$season <- as.factor(data$season)
data$episode <- as.factor(data$episode)
head(data)
```

* We merge our datasets. 

```{r}
# add information in about writers
writers <- transcripts %>%
  dplyr::select(episode, season, writer) %>%
  distinct()

data <- merge(data, writers, by=c("season", "episode"))

# add info about directors
directors <- transcripts %>% 
  dplyr::select(episode, season, director) %>%
  distinct()

data <- merge(data, directors, by = c("season", "episode"))
```

```{r}
data$Mindy_Kaling <- ifelse(str_detect(data$writer, "Mindy Kaling"), 1, 0)
data$Paul_Lieberstein <- ifelse(str_detect(data$writer, "Paul Lieberstein"), 1, 0)
data$B.J._Novak <- ifelse(str_detect(data$writer, "B.J. Novak"), 1, 0)
data$Michael_Schur <- ifelse(str_detect(data$writer, "Michael Schur"), 1, 0)

data$Mindy_Kaling <- as.factor(data$Mindy_Kaling)
data$Paul_Lieberstein <- as.factor(data$Paul_Lieberstein)
data$B.J._Novak <- as.factor(data$B.J._Novak)
data$Michael_Schur <- as.factor(data$Michael_Schur)

data$Paul_Feig <- ifelse(str_detect(data$writer, "Paul Feig"), 1, 0)
data$Randall_Einhorn <- ifelse(str_detect(data$writer, "Randall Einhorn"), 1, 0)
data$Greg_Daniels <- ifelse(str_detect(data$writer, "Greg Daniels"), 1, 0)
data$Ken_Kwapis <- ifelse(str_detect(data$writer, "Ken Kwapis"), 1, 0)

print(sum(data$Paul_Feig))
print(sum(data$Randall_Einhorn))
print(sum(data$Greg_Daniels))
print(sum(data$Ken_Kwapis))

data$Paul_Feig <- as.factor(data$Paul_Feig)
data$Randall_Einhorn <- as.factor(data$Randall_Einhorn)
data$Greg_Daniels <- as.factor(data$Greg_Daniels)
data$Ken_Kwapis <- as.factor(data$Ken_Kwapis)
```

* We notice that our data is on very different scales. To curve this issue, we divide the number of lines said by each character per episode by 100. 


```{r}
# scale lines said by each character
for (i in 3:29){
   data[,i] = data[,i]/100
}
```

```{r}
# encode first and last episode to column 
data$firstep <- ifelse(data$episode == 1, 1, 0)
data$last <- 0
data$last[data$season == 1 & data$episode == 6] <- 1
data$last[data$season == 2 & data$episode == 22] <- 1
data$last[data$season == 3 & data$episode == 24] <- 1
data$last[data$season == 4 & data$episode == 18] <- 1
data$last[data$season == 5 & data$episode == 28] <- 1
data$last[data$season == 6 & data$episode == 26] <- 1
data$last[data$season == 7 & data$episode == 25] <- 1
data$last[data$season == 8 & data$episode == 24] <- 1
data$last[data$season == 9 & data$episode == 24] <- 1
```

```{r}
# drop extra columns 
data = subset(data, select = -c(num_voters))
```

```{r}
head(data)
```


# Model Selection
```{r}
# initial model 
m1 <- lm(rating ~ season + firstep + last + lines_Michael + lines_Jim + lines_Pam + lines_Dwight + s_Michael + s_Jim + s_Pam + s_Dwight , data = data)
summary(m1)
```

```{r}
vif(m1)
plot(m1)
```


# Stepwise Selection
```{r}
# step on initial model + supporting characters
m_support <- lm(rating ~  season + firstep + last + lines_Michael + lines_Jim + lines_Pam + lines_Dwight + lines_Nellie + lines_Stanley + lines_Toby + lines_Gabe + lines_Ryan + lines_Karen + lines_Robert + s_Michael + lines_Andy + lines_Jan + lines_Todd + s_Jim + s_Pam + s_Dwight + s_Nellie + s_Stanley + s_Toby + s_Gabe + s_Ryan + s_Karen + s_Robert + s_Andy + s_Jan + s_Todd, data = data)

ols_step_both_aic(m_support)
```

```{r}
# m support summary
m_support <- lm(rating ~ season + last + lines_Michael + lines_Jim + lines_Dwight + lines_Nellie + lines_Stanley + s_Gabe + s_Pam + s_Stanley + s_Ryan + s_Toby + s_Andy + lines_Dwight + s_Michael + lines_Todd, data = data)

summary(m_support)
```

```{r}
m_writer <- lm(rating ~ season + last + lines_Michael + lines_Jim + lines_Dwight + lines_Nellie + lines_Stanley + s_Gabe + s_Pam + s_Stanley + s_Ryan + s_Toby + s_Andy + lines_Dwight + Mindy_Kaling + B.J._Novak + Paul_Lieberstein + Michael_Schur, data = data)

ols_step_both_aic(m_writer)
```


```{r}
# step on model w/ interactions
m_interactions <- lm(rating ~ season + last + lines_Michael + lines_Jim + lines_Dwight + lines_Nellie + lines_Stanley + s_Gabe + s_Pam + s_Stanley + s_Ryan + s_Toby + s_Andy + lines_Dwight + lines_Dwight*lines_Jim + lines_Dwight*lines_Angela + lines_Jim*lines_Pam + lines_Michael*lines_Ryan + lines_Erin*lines_Gabe + lines_Michael*lines_Holly + lines_Michael*lines_Pam + lines_Michael*lines_Jan + lines_Oscar*lines_Angela + lines_Andy*lines_Robert + s_Dwight*s_Angela + s_Andy*s_Robert + s_Pam*s_Michael, data = data)

ols_step_both_aic(m_interactions)
```

```{r}
m_interactions <- lm(rating ~ season + last + lines_Michael + lines_Nellie + lines_Stanley + s_Gabe + s_Pam + s_Stanley + s_Ryan + s_Toby + s_Andy + lines_Dwight*lines_Jim + s_Andy*s_Robert, data = data)

summary(m_interactions)
```



```{r}
interactions <- formula(lm(rating ~ season + first + last + lines_Michael + lines_Jim + lines_Dwight + lines_Pam + lines_Nellie + s_Michael + s_Jim + s_Pam + s_Dwight + lines_Stanley + s_Stanley + lines_Nellie + s_Toby + s_Gabe + s_Andy + s_Ryan + s_Robert +  lines_Jim*lines_Dwight + lines_Pam*s_Michael + lines_Jim*lines_Pam + lines_Dwight*lines_Angela + lines_Erin*lines_Andy + lines_Holly*lines_Michael, data))

v2.model <- step(v1.model, direction = "forward", scope = list(lower = v1.model, upper = interactions))

writers <- formula(lm(rating ~ season + first + last + lines_Michael + lines_Jim + lines_Dwight + lines_Pam + lines_Nellie + s_Michael + s_Jim + s_Pam + s_Dwight + lines_Stanley + s_Stanley + lines_Nellie + s_Toby + s_Gabe + s_Andy + s_Ryan + s_Robert +  lines_Jim*lines_Dwight + Mindy_Kaling + B.J._Novak + Paul_Lieberstein + Michael_Schur, data))

final.model <- step(v2.model, direction = "forward", scope = list(lower = v2.model, upper = writers))
```

```{r}
summary(final.model)
plot(final.model)
```

# Cross Validation
```{r}
IDs = seq(1,186)

# 80 - 20 test split
test_size = 5 

MSEs = c()
MAEs = c()

set.seed(0)
for(i in 1:test_size){
  set.seed(1)
  train_IDs = sample(IDs, 148)
  train = data_ratings[train_IDs,]
  test = data_ratings[-train_IDs,]
  
  our_model = lm(rating ~ season + lines_Michael + lines_Jim + lines_Pam + lines_Dwight + 
    s_Michael + s_Jim + s_Pam + s_Dwight + lines_Nellie + lines_Stanley + 
    s_Stanley + s_Andy + lines_Toby + s_Gabe + s_Toby + season*s_Michael, data=train)
  
  predictions = predict(our_model, test)
  residuals = predictions - test$rating
  MSE = mean(residuals^2)
  MAE = abs(residuals)
  MSEs = c(MSEs, MSE)
  MAEs = c(MAEs, MAE)
}
```

```{r}
print(mean(MSEs))
print(mean(MAEs))
```

# Code below was not discussed in this submission 
```{r model2}
# complete forward selection
#full.model <- formula(lm(rating ~ season + lines_Michael + lines_Jim + lines_Dwight + lines_Nellie + s_Michael + s_Pam + s_Dwight + s_Stanley + episode + lines_Angela + lines_Jan + lines_Kevin + lines_Oscar + lines_Phyllis + lines_Roy + lines_Ryan + lines_Stanley + lines_Kelly + lines_Toby + lines_Meredith + lines_Darryl + lines_Creed + lines_Andy + lines_Karen + lines_Holly + lines_Erin + lines_Gabe + s_Angela + s_Jan + s_Kevin + s_Oscar + s_Phyllis + s_Roy + s_Ryan + s_Kelly + s_Toby + s_Meredith + s_Darryl + s_Creed + s_Andy + s_Karen + s_Holly + s_Erin + s_Gabe + s_Nellie + Mindy_Kaling + Paul_Lieberstein + B.J._Novak + Michael_Schur + season*lines_Michael + season*s_Michael + season*lines_Pam + season*s_Pam + season*lines_Jim + season*s_Jim + season*lines_Dwight + season*s_Dwight + season*s_Stanley, data_ratings))

#fwd.model <- step(v2.model, direction = 'forward', scope = list(lower = final.model, upper = full.model))
```

```{r}
#summary(fwd.model)
```

